%کلمات کلیدی انگلیسی
\latinkeywords{Human Activity Recognition, Self-Supervised Learning, Wavelet Transform, Contrastive Learning, Transfer Learning}
%چکیده انگلیسی

\en-abstract{With the increasing expansion of smart environments and the use of various sensors such as mobile phones, the need for systems that can automatically and accurately recognize human activities has grown. One of the main challenges in this field is the heavy reliance of machine learning models on labeled data, the collection of which on a large scale is costly and time-consuming. This issue highlights the necessity of utilizing methods that can extract conceptual and transferable representations from sensor data without the need for manual labeling. In this research, a self-supervised learning framework has been designed that, by leveraging a combination of temporal and frequency perspectives, attempts to extract high-quality and general representations from raw human activity data. The proposed framework, aiming to improve data representation quality, reduce the need for labeled data, and enhance model generalizability, has been evaluated in two different scenarios: first, training and evaluation in the same environment; and second, training in one environment and evaluating in a different one, with the goal of assessing the model's knowledge transfer and generalization capabilities. The evaluation results show that the proposed framework has achieved \textbf{92.3\% F1 score} (with a \textbf{0.9\% improvement} over the base model) in the direct training scenario on the HAPT dataset, and \textbf{90.2\% F1 score} (with a \textbf{1.5\% improvement} over the base model) in the transfer learning scenario from the MobiAct dataset to the HAPT dataset. By utilizing the combination of temporal and frequency information, this framework has been able to extract representations that have led to improved accuracy in human activity recognition. Overall, the proposed method takes an effective step towards reducing dependency on labeled data and developing generalizable models for application in diverse and real-world environments.}
%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}

\een-abstract

\vspace*{.5cm}
{\noindent\large\textbf{Key Words:}}\par
\vspace*{.5cm}
\noindent\elatinkeywords
\end{latin}